openarchaeoCollaboration

### 2023-01-30 analysis/paper.qmd
Community detection visuals

```{r plot-graph-repo-repo}
oarch_graph_repo_repo <- tbl_graph(nodes_repos(oarch_graph, category),
                                   edges_common_users(oarch_graph))

@@

```{r iplot-graph-repo-repo}
iplot <- oarch_graph_repo_repo |>
    ggraph(layout = "graphopt") +
    geom_edge_link(aes(alpha = n)) +
    geom_point_interactive(aes(x, y, colour = category, tooltip = repo)) + 
    scale_edge_alpha(trans = "log") +
    labs(edge_alpha = "Common contributors") +
    theme_graph()

@@

>>>>

```{r plot-graph-repo-repo}
oarch_graph_repo_repo <- tbl_graph(nodes_repos(oarch_graph, category, tags),
                                   edges_common_users(oarch_graph))

@@

```{r plot-graph-repo-repo-edge-betweenness}
oarch_graph_repo_repo <- tbl_graph(nodes_repos(oarch_graph,category,tags),
                                   edges_common_users(oarch_graph),
                                   directed = FALSE)

oarch_graph_repo_repo |>
  mutate(degree = centrality_degree()) |>
  filter(degree > 1) |>
  mutate(group = as.character(group_edge_betweenness())) ->
  oarch_graph_repo_repo

iplot <- oarch_graph_repo_repo |>
  ggraph(layout = "graphopt") +
  geom_edge_link(aes(alpha = n)) +
  #geom_node_point(aes(colour = group)) +
  #geom_node_text(aes(label = group)) +
  geom_point_interactive(aes(x, y, colour = group, tooltip = repo)) + 
  scale_edge_alpha(trans = "log") +
  labs(edge_alpha = "Common contributors")

@@

```{r plot-graph-repo-repo-edge-betweenness-dendrogram}
oarch_graph_repo_repo <- tbl_graph(nodes_repos(oarch_graph),
                                   edges_common_users(oarch_graph),
                                   directed = TRUE)

oarch_graph_repo_repo |>
  mutate(degree = centrality_degree()) |>
  filter(degree > 1) |>
  mutate(group = as.character(group_edge_betweenness())) ->
  oarch_graph_repo_repo

xx <- igraph::edge.betweenness.community(oarch_graph_repo_repo)
xx <- as.dendrogram(xx)
plot(xx)

ggraph(xx, 'dendrogram', height = height)

```{r plot-graph-repo-repo-louvain}
oarch_graph_repo_repo <- tbl_graph(nodes_repos(oarch_graph),
                                   edges_common_users(oarch_graph),
                                   directed = FALSE)

oarch_graph_repo_repo |>
  mutate(degree = centrality_degree()) |>
  filter(degree > 1) |>
  mutate(group = as.character(group_louvain())) ->
  oarch_graph_repo_repo

oarch_graph_repo_repo |>
  ggraph(layout = "graphopt") +
  geom_edge_link(aes(alpha = n)) +
  geom_node_point(aes(colour = group)) +
  scale_edge_alpha(trans = "log") +
  labs(edge_alpha = "Common contributors")
```
